No Correlations were Found between the efforts made by the Staff of Toronto's Central Intake Line and Toronto;s Homeless Death Counts

### 2024-01-22 outputs/paper/paper.qmd
created Abstract for paper and added a table of content to the output. Test rendered to observe whether action to add toc has succeeded.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sandy Yu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

>>>>

---
title: "No Correlations were Found between the efforts made by the Staff of Toronto's Central Intake Line and Toronto;s Homeless Death Counts"
subtitle: "My subtitle if needed"
author: 
  - Sandy Yu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "For the Government of Toronto, the physical well-being of Toronto’s local homeless population has always been one of its primary focuses. Numerous social efforts, funded by the government, were made in attempts to reduce the death rate of the local homeless population. In order to understand the magnitude of social impact created by the Government of Toronto, analyses were performed to investigate the correlation between the efforts made by the staff of Toronto’s Central Intake Line and the monthly homeless death counts between November 2020 to June 2023 using data from OpenDataToronto. Staff efforts such as the number of calls coded, number of referral to shelter, and number of information for homelessness prevention, were documented and compared against the monthly homeless death counts. No discernible correlations were found between each of these efforts to the monthly homeless death counts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
library(dplyr)
library(lubridate)
library(zoo)
```
